Proposal to improve BBC Search through the use of Linked Data

### 2014-05-05 chapter3.tex
Starting drilling into the different content items.

The front end search application currently divides all the searchable
content into so-called ``zones'',

>>>>

The front end search application currently divides all the searchable
content into so-called ``zones'':

%TODO - is this all of them?
\begin{itemize}
  \item About the BBC
  \item Blogs
  \item CBBC
  \item Films
  \item Food
  \item Gardening
  \item Health \& Parenting 
  \item History
  \item iPlayer
  \item Learning
  \item Local (archive)
  \item Music
  \item News
  \item Ouch!
  \item Religion \& Ethics
  \item Science \& Nature
  \item Sport
  \item Teenagers
  \item TV \& Radio Programmes
  \item TV \& Radio Sites
\end{itemize}

Some of these zones or categories related to major, well-known areas of
BBC online. Some seem to be more esoteric or legacy areas, many of which
are obtained through a web crawler. The presence of ``iPlayer'',
``TV \& Radio Programmes'' and ``TV & Radio Sites'' is a distinction that
has arisen for technical and historic reasons, which is not likely to be
clear to users.

In the rest of this section, I will look at the nature of each category
of content, how it is currently collected for indexing and note any
obvious areas that might benefit from an improved approach to indexing.

\subsection{About the BBC}

The ``About the BBC'' category is a collection of subsites centred out
information about the BBC itself. Audience members can here find information
about making complaints, press releases, news about the BBC, blogs, etc.

This can be content that users will want to find via the search application.
The BBC homepage is focused around presented latest online content, but it
is with these more fringe areas of the BBC website that satisfy specific
needs (e.g. ``How do I complain about a programme?'') that the
search application can be of particular use.

There is a mix of static pages and time-based content such as blog posts.
One advantage of any part of the BBC website that hosts posts or articles,
is they are generally syndicated via RSS or Atom. This gives an opportunity
to follow for new updates in the same way the public would without any
need for bespoke integration work by the teams in charge of the content.
